\setchapterpreamble[u]{\margintoc}
\chapter{Class Options}
\labch{options}

In this chapter I will describe the most common options used, both the 
ones inherited from \Class{scrbook} and the \Class{kao}-specific ones. 
Options passed to the class modifies its default behaviour; beware 
though that some options may lead to unexpected results\ldots

\section{\Class{KOMA} Options}

The \Class{kaobook} class is based on \Class{scrbook}, therefore it 
understands all of the options you would normally pass to that class. If 
you have a lot of patience, you can read the \KOMAScript\xspace 
guide.\sidenote{The guide can be downloaded from 
\url{https://ctan.org/pkg/koma-script?lang=en}.} Actually, the reading 
of such guide is suggested as it is very instructive.

Every \KOMAScript\xspace option you pass to the class when you load it 
is automatically activated. In addition, in \Class{kaobook} some options 
have modified default values. For instance, the font size is 9.5pt and 
the paragraphs are separated by space,\sidenote[][-7mm]{To be precise, 
they are separated by half a line worth of space: the \Option{parskip} 
value is \enquote{half}.} not marked by indentation.

\section{\Class{kao} Options}

In the future I plan to add more options to set the paragraph formatting 
(justified or ragged) and the position of the margins (inner or outer in 
twoside mode, left or right in oneside mode).\sidenote{As of now, 
paragraphs are justified, formatted with \Command{singlespacing} (from 
the \Package{setspace} package) and \Command{frenchspacing}.}

I take this opportunity to renew the call for help: everyone is 
encouraged to add features or reimplement existing ones, and to send me 
the results. You can find the GitHub repository at 
\url{https://github.com/fmarotta/kaobook}.

\begin{kaobox}[frametitle=To Do]
Implement the \Option{justified} and \Option{margin} options. To be 
consistent with the \KOMAScript\xspace style, they should accept a 
simple switch as a parameter, where the simple switch should be 
\Option{true} or \Option{false}, or one of the other standard values for 
simple switches supported by \KOMAScript. See the \KOMAScript\xspace 
documentation for further information.
\end{kaobox}

The above box is an example of a \Environment{kaobox}, which will be 
discussed more thoroughly in \frefch{mathematics}. Throughout the book I 
shall use these boxes to remarks what still needs to be done.

\section{Other Things Worth Knowing}

A bunch of packages are already loaded in the class because they are 
needed for the implementation. These include:

\begin{itemize}
	\item etoolbox
	\item calc
	\item xifthen
	\item xkeyval
	\item xparse
	\item xstring
\end{itemize}

Many more packages are loaded, but they will be discussed in due time. 
Here, we will mention only one more set of packages, needed to change 
the paragraph formatting (recall that in the future there will be 
options to change this). In particular, the packages we load are:

\begin{itemize}
	\item ragged2e
	\item setspace
	\item hyphenat
	\item microtype
	\item needspace
	\item xspace
	\item xcolor (with options \Option{usenames,dvipsnames})
\end{itemize}

Some of the above packages do not concern paragraph formatting, but we 
nevertheless grouped them with the others. By default, the main text is 
justified and formatted with singlespacing and frenchspacing; the margin 
text is the same, except that the font is a bit smaller.

As a last warning, please be aware that the \Package{cleveref} package 
is not compatible with \Class{kaobook}. You should use the commands 
discussed in \refsec{hyprefs} instead.

\section{Document Structure}

We provide optional arguments to the \Command{title} and 
\Command{author} commands so that you can insert short, plain text 
versions of this fields, which can be used, typically in the half-title 
or somewhere else in the front matter, through the commands 
\Command{@plaintitle} and \Command{@plainauthor}, respectively. The PDF 
properties \Option{pdftitle} and \Option{pdfauthor} are automatically 
set by hyperref to the plain values if present, otherwise to the normal 
values.\sidenote[][*-1]{We think that this is an important point so 
we remark it here. If you compile the document with pdflatex, the PDF 
metadata will be altered so that they match the plain title and author 
you have specified; if you did not specify them, the metadata will be 
set to the normal title and author.}

There are defined two page layouts, \Option{margin} and \Option{wide}, 
and two page styles, \Option{plain} and \Option{fancy}. The layout 
basically concern the width of the margins, while the style refers to 
headers and footer; these issues will be 
discussed in \frefch{layout}.\sidenote[][6mm]{For now, suffice it to say that pages with 
the \Option{margin} layout have wide margins, while with the 
\Option{wide} layout the margins are absent. In \Option{plain} pages the 
headers and footer are suppressed, while in \Option{fancy} pages there 
is a header.} 

The commands \Command{frontmatter}, \Command{mainmatter}, and 
\Command{backmatter} have been redefined in order to automatically 
change page layout and style for these sections of the book. The front 
matter uses the \Option{margin} layout and the \Option{plain} page 
style. In the mainmatter the margins are wide and the headings are 
fancy. In the appendix the style and the layout do not change; however 
we use \Command{bookmarksetup\{startatroot\}} so that the bookmarks of 
the chapters are on the root level (without this, they would be under 
the preceding part). In the backmatter the margins shrink again and we 
also reset the bookmarks root.
